Measuring security performance in the Android ecosystem

### 2015-06-08 security_scoring.tex
Rework description of full_comp figure

\daTabSecScoresmodel
Even within device manufacturers, different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \emph{\daSecScoreBestmodel} (\daSecScoreBestmodelScore\ out of 10) scoring highest and \emph{\daSecScoreWorstmodel} (\daSecScoreWorstmodelScore\ out of 10) scoring lowest.
We can then test whether this seems fair by comparing the version data for the highest and lowest scoring models.
Figure~\ref{fig:full_version_comp}c shows the full version distribution for \emph{\daSecScoreWorstmodel}, Figure~\ref{fig:full_version_comp}b shows the full version distribution for \emph{HTC Desire HD A9191} which used to be our worst model and for which we have more historical data and Figure~\ref{fig:full_version_comp}a shows the same for \emph{\daSecScoreBestmodel}.
There is a marked difference in the distribution of updates between the best and worst with only \daSecScoreWorstmodelNumFullVersions\ full version for \emph{\daSecScoreWorstmodel}, 2 full versions for \emph{HTC Desire HD A9191} and \daSecScoreBestmodelNumFullVersions\ for \emph{\daSecScoreBestmodel}.
Both \emph{Galaxy Nexus} and \emph{HTC Desire HD A9191} device models start off with the full version string of `2.3.3 GRI40' but the \emph{\daSecScoreBestmodel} receives many more updates over the same time period.
Other models from the same manufacturer with similar model names to \emph{HTC Desire HD A9191} do much better such as the \emph{Desire HD}.

>>>>

\daTabSecScoresmodel
Even within device manufacturers, different models can have very different update behaviours and hence security.
Table~\ref{tab:sec_model} shows the results for the \daNumSigModels\ device models which have a significant presence by the same metric with \emph{\daSecScoreBestmodel} (\daSecScoreBestmodelScore\ out of 10) scoring highest and \emph{\daSecScoreWorstmodel} (\daSecScoreWorstmodelScore\ out of 10) scoring lowest.
We can then test whether this seems fair by comparing the version data for the highest and lowest scoring models.
Figure~\ref{fig:full_version_comp}c shows the full version distribution for \emph{\daSecScoreWorstmodel} which we only observe running one version.
Figure~\ref{fig:full_version_comp}b shows the full version distribution for \emph{HTC Desire HD A9191} which used to be our worst model and for which we have more historical data, it shows how it received one update at the beginning of 2012 which was deployed fairly rapidly to most devices but received no further updates.
Figure~\ref{fig:full_version_comp}a shows the same information for \emph{\daSecScoreBestmodel} but it is very different with \daSecScoreBestmodelNumFullVersions\ different versions, some of which were only deployed to small numbers of devices but the distribution for all devices regularly and rapidly transitions from one version to another before ending up on `4.3 JWR66Y'.
Both \emph{Galaxy Nexus} and \emph{HTC Desire HD A9191} device models start off with the full version string of `2.3.3 GRI40' but the \emph{\daSecScoreBestmodel} receives many more updates over the same time period.
Other models from the same manufacturer with similar model names to \emph{HTC Desire HD A9191} do much better such as the \emph{Desire HD}.
